### 2016-09-25 paper/extended-example.tex

\subsection{Regular Bijective Lenses}
\afm{I'm not sure how necessary this section is.  While I want to give users a
  bit of idea about how things map between one another, I think this section
  might go into too much detail.  How would I be able to give the intuition of
  finding parts that map to each other, without just describing lenses (assuming
  that's the right sort of thing to do)?}
Once we have a synthesis specification, we need to find a lens that
will convert back and forth between formats and that satisfies the
given examples.  In this paper, we begin our work with a simple and 
relatively standard language of bijective string lens combinators.
In order to guarantee the functions generated by these combinators
form proper bijections between source and target, they are given types using
regular expressions.  We typically write
$\Lens \OfType \Regex \Leftrightarrow \RegexAlt$ to indicate that a lens $\Lens$
converts back and forth between data belonging
to the languages of regular expressions
$\Regex$ and $\RegexAlt$.

>>>>

\subsection{Regular Bijective Lenses}
\afm{I'm not sure how necessary this section is.  While I want to give users a
  bit of idea about how things map between one another, I think this section
  might go into too much detail.  How would I be able to give the intuition of
  finding parts that map to each other, without just describing lenses (assuming
  that's the right sort of thing to do)?}
\bcp{I suggest rearranging things a bit.  The problem I see here is that
  this section ends up duplicating material from section 3.  So why not put
  it after 3?  I.e., take the example in figure 1 (and the text up to this
  point) and put it in the intro.  Take the rest of this section, remove all
the explanations of what lenses are (or move them top the current section 3)
and move the rest to a new section after the current section 3 that just
focuses on synthesis.}
Once we have a synthesis specification, we need to find a lens that
will convert back and forth between formats and that satisfies the
given examples.  In this paper, we begin our work with a simple and 
relatively standard language of bijective string lens combinators.
In order to guarantee the functions generated by these combinators
form proper bijections between source and target, they are given types using
regular expressions.  We typically write
$\Lens \OfType \Regex \Leftrightarrow \RegexAlt$ to indicate that a lens $\Lens$
converts back and forth between data belonging
to the languages of regular expressions
$\Regex$ and $\RegexAlt$.

### 2016-09-25 paper/introduction.tex

Bidirectional programming is used heavily in practice.
Augeas~\cite{augeas}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
The language biXid~\cite{bixid} is developed for expressing bidirectional XML
transformations.
XSugar~\cite{xsugar} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{epidoc} and Leiden+~\cite{leidenplus} formats for
encoding ancient documents~\cite{epidocleidenplus}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.

>>>>

Bidirectional programming is used heavily in practice.\bcp{This may be
  overstating the case, for lenses per se.  Augeas is the only real-world
  example AFAIK.}
Augeas~\cite{?}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
The language biXid~\cite{bixid} is developed for expressing bidirectional XML
transformations.
XSugar~\cite{xsugar} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{epidoc} and Leiden+~\cite{leidenplus} formats for
encoding ancient documents~\cite{epidocleidenplus}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.
